Visual Inference Lineups

### 2020-01-12 paper/paper.tex

% Pandoc header
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\usepackage{graphicx}

@@

This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics. The choropleth map is the traditional approach for visualising aggregated statistics across administrative boundaries. A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location. The hexagon tile map builds on existing displays, such as the cartogram, and tesselated hexagon displays. It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons.

@@

The Australian Cancer Atlas (XXX ref) is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated. The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia. It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas. The hexagon tile map may be a useful alternative display for the atlas.

The algorithm to construct a hexagon tile map is available in the R package sugarbag (XXX ref). This type of display may be useful for other countries, and other purposes.

The paper is organised as follows. The next section

@@

Spatial visualisations communicate the distribution of statistics over geographic space. The most common display for spatial data is the choropleth map. It is used to present aggregated statistics for geographic units such as the population. Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{1}{]}.
Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
The rural communities in Australia operate on a much larger geographic space than small inner-city communities. When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base. This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{2}{]}. An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{3}{]}.
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.

@@

A cartogram transforms the geographic map base. The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit. There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{4}{]}, {[}\protect\hyperlink{ref-CBATCC}{1}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units. The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.

Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units. The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{5}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics. This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas. However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{4}{]} is another method that does not retain the boundaries of geographic units. Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population. The neighbour relationships can be illustrated by connecting the boundaries of the circles. A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{6}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{7}{]}.
These cartogram methods all allow two variables to be shown in the single display. these methods are discussed further in XXX cite review paper

@@

To test these hypotheses, the line up protocol randomly places a ``guilty'' data visualisation in a lineup of ``innocents''. Where the guilty data set contains structure, and the innocents data sets do not.
In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{8}{]}.
The guilty data is identified as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account account for the guilty data set. When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a \(1/m\) chance or type I error of being wrong.

The lineup protocol can be used in a variety of testing scenarios for visualisations. {[}\protect\hyperlink{ref-GIIV}{9}{]} suggest the choropleth map for testing spatial structure in a data set. The lineup protocol allows for flexibility in the definition of null data. In the case of spatial visualisations it is likely that neighbours are related to some degree. To account for this, null data sets can be generated by sampling from a known model that accounts for spatial covariance.

@@

Participants were able to choose to participate by selecting this task from the list of tasks available to them.
There were 95 participants involved in the study. All of these participants read the introductory materials and viewed example questions before proceeding to the survey. Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in appendix section regarding \protect\hyperlink{training}{training}.
All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.

@@

Data was collected through a web application containing the online survey.
Each participant used the internet to access the survey.
The data collection took place using a secure link between the survey web application and the googlesheet used to store results. The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{10}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.

@@

The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{11}{]} as this is the common display for spatial cancer data.
Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
A line up protocol was implemented to arrange \(N\) maps in each display.
A reasonable amount of null plots \(N-1\) in the lineup was chosen to ensure the real data map was well hidden. A reasonable number of plots to show in each lineup, \(N = 12\) was chosen to not overwhelm participants due to the detailed choropleth maps of Australian SA3 areas.

@@

The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{12}{]}.

@@

The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
The R {[}\protect\hyperlink{ref-RCore}{12}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{13}{]} package implements generalised linear mixed effect models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:

@@

Computation will be done using R {[}\protect\hyperlink{ref-RCore}{12}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{13}{]}.

@@

Fig. \ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model. Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table. \ref{tab:exp-design}; the detection rates for each display are connected by a line segment. The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts. One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix \protect\hyperlink{lineups}{Lineups} section. Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map. We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.

@@

\hypertarget{choices}{%
\subsection{Choices}\label{choices}}

The choices made by participants are examined in Fig. \ref{fig:choices}.
Participants were misled by the choropleth display, but not the hexagon display for All Cities displays except (2). The maps with a North West to South East trend was chosen with much greater frequency in all displays. All of Three Cities displays, except (4), were detected in the hexagon display. All except one lineup had at least one participant select the correct map in the lineup as shown in Fig. \ref{fig:choices}.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/choices-1.pdf}
\caption{\label{fig:choices}Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup. The points coloured orange show the map which contained a trend model, these are the correct choices. The numbers differentiate the replicates of each trend model and type of map display. Participants were able to select 0 to indicate they did not want to choose a map.}
\end{figure}

@@

\hypertarget{training}{%
\subsection{Training}\label{training}}

The participants were trained using three displays. There were relatively simple lineups and are shown in Fig. \ref{fig:training1} and Fig. \ref{fig:training2}.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/training1-1.pdf}
\caption{\label{fig:training1}The training lineups of choropleth maps.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/training2-1.pdf}
\caption{\label{fig:training2}The training lineups of hexagon tile maps.}
\end{figure}

\hypertarget{survey-application}{%
\subsection{Survey application}\label{survey-application}}

The survey application was hosted on a website external to the Figure-Eight platform. Following suggestions in the documentation, the information and training required for a participant to make a decision was included that survey

The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Fig. \ref{fig:survey-demogs}.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/survey-demogs-1.pdf}
\caption{\label{fig:survey-demogs}The demographics questions tab of the shinydashboard survey application.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/survey-hex-1.pdf}
\caption{\label{fig:survey-hex}An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/survey-choro-1.pdf}
\caption{\label{fig:survey-choro}An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.}
\end{figure}

\hypertarget{lineups}{%
\subsection{Lineups}\label{lineups}}

Replicate 3 of the All Cities distribution is shown in Figures . The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map. Many maps in the Choropleth lineup (a) are coloured yellow, two are half light blue, and two are obviously blue. Only one of the maps looks red.

Lineups were created using the Australian Statistical Areas at Level 3.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/cities-geo-1.pdf}
\caption{\label{fig:cities-geo}The lineup of choropleth map displays hides a distribution that affects all capital cities.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/cities-hex-1.pdf}
\caption{\label{fig:cities-hex}The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. Replicate (2) for All Cities.}
\end{figure}

The higher values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. There were no other choropleth maps that were coloured as blue as map (3). This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
The same data showed in the hexagon tile map display shows varied distributions across the lineup. They are more diverse in colour than the choropleth counterparts. The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons. For different reasons the participants were able to make the same correct choice.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-CBATCC}{}%
1. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246

\leavevmode\hypertarget{ref-CTTMB}{}%
2. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174

\leavevmode\hypertarget{ref-NISCC}{}%
3. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401

\leavevmode\hypertarget{ref-ACTUC}{}%
4. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260

\leavevmode\hypertarget{ref-NAC}{}%
5. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380

\leavevmode\hypertarget{ref-RSCW}{}%
6. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10

\leavevmode\hypertarget{ref-CDWCS}{}%
7. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224

\leavevmode\hypertarget{ref-GTPCCD}{}%
8. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448

\leavevmode\hypertarget{ref-GIIV}{}%
9. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979

\leavevmode\hypertarget{ref-sheets}{}%
10. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.

\leavevmode\hypertarget{ref-VVSIALM}{}%
11. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956

\leavevmode\hypertarget{ref-RCore}{}%
12. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-lme4}{}%
13. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48

>>>>

% Pandoc header
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics. The choropleth map is the traditional approach for visualising aggregated statistics across administrative boundaries. A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location. The hexagon tile map builds on existing displays, such as the cartogram, and tesselated hexagon displays. It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons. The algorithm to construct a hexagon tile map is available in the R package sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}. This type of display may be useful for other countries, and other purposes.

@@

The Australian Cancer Atlas {[}\protect\hyperlink{ref-atlas}{2}{]} is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated. The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia. It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas. The hexagon tile map may be a useful alternative display for the atlas.

The experiment was conducted using the lineup protocol, a visual inference procedure {[}\protect\hyperlink{ref-GIIV}{3}{]}, to objectively test the effectiveness of the two displays.

The paper is organised as follows. The next section discusses the background of geographic data display and visual inference procedures. The \protect\hyperlink{methodology}{Methodology} Section describes the methods for conducting the experiment and analysing the results. The results are summarized in Section \protect\hyperlink{results}{Results}.

@@

Spatial visualisations communicate the distribution of statistics over geographic space. The most common display for spatial data is the choropleth map. It is used to present aggregated statistics for geographic units such as the population. Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{4}{]}.
Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
The rural communities in Australia operate on a much larger geographic space than small inner-city communities. When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base. This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{5}{]}. An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{6}{]}.
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.

@@

A cartogram transforms the geographic map base. The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit. There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{4}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units. The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.

Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units. The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics. This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas. However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} is another method that does not retain the boundaries of geographic units. Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population. The neighbour relationships can be illustrated by connecting the boundaries of the circles. A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.

@@

To test these hypotheses, the line up protocol randomly places a ``guilty'' data visualisation in a lineup of ``innocents''. Where the guilty data set contains structure, and the innocents data sets do not.
In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{11}{]}.
The guilty data is identified as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account account for the guilty data set. When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a \(1/m\) chance or type I error of being wrong.

The lineup protocol can be used in a variety of testing scenarios for visualisations. {[}\protect\hyperlink{ref-GIIV}{3}{]} suggest the choropleth map for testing spatial structure in a data set. The lineup protocol allows for flexibility in the definition of null data. In the case of spatial visualisations it is likely that neighbours are related to some degree. To account for this, null data sets can be generated by sampling from a known model that accounts for spatial covariance.

@@

Participants were able to choose to participate by selecting this task from the list of tasks available to them.
There were 95 participants involved in the study. All of these participants read the introductory materials and viewed example questions before proceeding to the survey. Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in appendix section regarding {[}training{]}.
All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.

@@

Data was collected through a web application containing the online survey.
Each participant used the internet to access the survey.
The data collection took place using a secure link between the survey web application and the googlesheet used to store results. The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{12}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.

@@

The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{13}{]} as this is the common display for spatial cancer data.
Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
A line up protocol was implemented to arrange \(N\) maps in each display.
A reasonable amount of null plots \(N-1\) in the lineup was chosen to ensure the real data map was well hidden. A reasonable number of plots to show in each lineup, \(N = 12\) was chosen to not overwhelm participants due to the detailed choropleth maps of Australian SA3 areas.

@@

The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{14}{]}.

@@

The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
The R {[}\protect\hyperlink{ref-RCore}{14}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{15}{]} package implements generalised linear mixed effect models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:

@@

Computation will be done using R {[}\protect\hyperlink{ref-RCore}{14}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{15}{]}.

@@

Fig. \ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model. Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table. \ref{tab:exp-design}; the detection rates for each display are connected by a line segment. The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts. One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix {[}Lineups{]} section. Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map. We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.

@@

@@

@@

\hypertarget{acknowledgment-1}{%
\section{Acknowledgment}\label{acknowledgment-1}}

The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations. They would also like to thank Distinguished Professor Kerrie Mengersen and Doctor Earl Duncan for suggestions and comments.

The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/tree/master/paper}{GitHub}.
Supplementary materials have been included to discuss the survey procedures,

The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{14}{]} with the use of the following packages:
- For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{16}{]}, rticles {[}\protect\hyperlink{ref-rticles}{17}{]}, knitr {[}\protect\hyperlink{ref-knitr}{18}{]}.
- For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{19}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{20}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{21}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{22}{]}.
- For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{23}{]}, png {[}\protect\hyperlink{ref-png}{24}{]}, grid {[}\protect\hyperlink{ref-grid}{25}{]}.
- For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{15}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{26}{]}.

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-sugarbag}{}%
1. Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps.

\leavevmode\hypertarget{ref-atlas}{}%
2. Queensland CC Australian Cancer Atlas (https://atlas.cancer.org.au).

\leavevmode\hypertarget{ref-GIIV}{}%
3. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979

\leavevmode\hypertarget{ref-CBATCC}{}%
4. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246

\leavevmode\hypertarget{ref-CTTMB}{}%
5. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174

\leavevmode\hypertarget{ref-NISCC}{}%
6. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401

\leavevmode\hypertarget{ref-ACTUC}{}%
7. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260

\leavevmode\hypertarget{ref-NAC}{}%
8. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380

\leavevmode\hypertarget{ref-RSCW}{}%
9. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10

\leavevmode\hypertarget{ref-CDWCS}{}%
10. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224

\leavevmode\hypertarget{ref-GTPCCD}{}%
11. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448

\leavevmode\hypertarget{ref-sheets}{}%
12. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.

\leavevmode\hypertarget{ref-VVSIALM}{}%
13. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956

\leavevmode\hypertarget{ref-RCore}{}%
14. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-lme4}{}%
15. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48

\leavevmode\hypertarget{ref-rmarkdown}{}%
16. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida

\leavevmode\hypertarget{ref-rticles}{}%
17. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.

\leavevmode\hypertarget{ref-knitr}{}%
18. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research

\leavevmode\hypertarget{ref-tidyverse}{}%
19. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686

\leavevmode\hypertarget{ref-nullabor}{}%
20. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.

\leavevmode\hypertarget{ref-ggthemes}{}%
21. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.

\leavevmode\hypertarget{ref-RColorBrewer}{}%
22. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.

\leavevmode\hypertarget{ref-cowplot}{}%
23. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.

\leavevmode\hypertarget{ref-png}{}%
24. Urbanek S (2013) Png: Read and write png images.

\leavevmode\hypertarget{ref-grid}{}%
25. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-kableExtra}{}%
26. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.

### 2020-01-12 paper/supplementary/lineups.Rmd

---
title: "Visual Inference Lineups"
author: "Stephanie Kobakian and Dianne Cook"
output: pdf_document
---

@@

```{r data}
library(tidyverse)
library(cowplot)
library(png)
library(grid)
library(lme4)
library(ggthemes)
library(RColorBrewer)
library(knitr)
library(kableExtra)

@@

@@

```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/aus_cities_4_geo.png")))
```

>>>>

---
title: "Visual Inference Lineups"
author: "Stephanie Kobakian and Dianne Cook"
output: bookdown::pdf_document
link_citatons: true
---

@@

```{r data}

library(tidyverse)
library(readxl)
library(cowplot)
library(png)
library(grid)
library(lme4)
library(ggthemes)
library(RColorBrewer)
library(knitr)
library(kableExtra)

@@

```{r}
choice_tabs <- d %>% 
  count(trend, type, choice, replicate, choice, detect) %>% 
  group_by(trend, type, replicate) %>% 
  mutate(prop = round(n/sum(n), 2)) %>% 
  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
  mutate(bottom = 0) %>% 
  select(Trend = trend, Rep = replicate, Type = type, prop, choice) %>% 
  spread(choice, prop, fill = "0") %>% 
  nest(-Trend)
```

```{r choice-nwse}
knitr::kable(choice_tabs$data[[1]], format = "latex", align = "rrrrrrrrrrrrrr",
  caption = "NW-SE") %>%
  collapse_rows(., columns = c(1,2))
```

```{r choice-three}
knitr::kable(choice_tabs$data[[2]], format = "latex", align = "rrrrrrrrrrrrrr",
  caption = "Three Cities") %>%
  collapse_rows(., columns = c(1,2))
```

```{r choice-all}
knitr::kable(choice_tabs$data[[3]], format = "latex", align = "rrrrrrrrrrrrrr",
  caption = "All Cities") %>%
  collapse_rows(., columns = c(1,2))
```

@@

```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 5, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/aus_cities_4_geo.png")))
```
